Real-Time Activity Classification by Matched Filtering using Body-Worn Accelerometers

### 2016-10-29 notes/poster/example.tex
Incrimentals

\documentclass{sciposter}
\usepackage{lipsum}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{graphicx,url}
\usepackage[english]{babel}   
\usepackage[utf8]{inputenc}
%\usepackage{fancybullets}
\newtheorem{Def}{Definition}

@@

\begin{center}
 \includegraphics[scale=.75]{reference_pulse_32Hz_4sec_8downsample_2.png}
\end{center}

%%%%%%%%%%%%%%%
% Performance %
%%%%%%%%%%%%%%%
\section{Performance}
The Kinetisense sensor was used for the algorithm performance analysis in this paper.
This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user.
A separate instance of walking data was used specifically for training the classifier.
%
%\begin{figure}[!ht]
%  %\captionsetup[subfigure]{labelformat=empty}
%  \centering
%  \subfloat[\label{fig:frac_walking_jogging}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_jogging.png}}
%  \quad
%  \centering
%  \subfloat[\label{fig:frac_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{fraction_threshold_walking_to_bicycling.png}}
%  \centering
%  \quad
%  \subfloat[\label{fig:roc_walking_jogging}]{\includegraphics[width=0.45\textwidth]{ROC_walk_to_run.png}}
%  \centering
%  \quad
%  \subfloat[\label{fig:roc_walking_bicycling}]{\includegraphics[width=0.45\textwidth]{ROC_walk_to_bike.png}}
%  \caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking. Results produced at decimation 8. Figures (c) and (d) are the corresponding ROC curves produced from (a) and (b) respectively.}
%  \label{fig:MF_performance}
%\end{figure}

>>>>

\documentclass{sciposter}
\usepackage{lipsum}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{graphicx,url}
\usepackage[english]{babel}   
\usepackage[utf8]{inputenc}
%\usepackage{fancybullets}
\newtheorem{Def}{Definition}

@@

%%%%%%%%%%%%%%%
% Performance %
%%%%%%%%%%%%%%%
\section{Performance}
The Kinetisense sensor was used for the algorithm performance analysis in this paper.
This unit has a three-axis accelerometer with an acceleration range of -5g to +5g and a sampling rate of 128Hz.
Samples of walking, jogging, and bicycling have been recorded with this unit attached to the ankle of the user.
A separate instance of walking data was used specifically for training the classifier.

\begin{figure}[!ht]

\centering
\subfigure[Jogging]{\includegraphics[width=0.35\textwidth]{fraction_threshold_walking_to_jogging.png}}
\subfigure[Bicycling]{\includegraphics[width=0.35\textwidth]{fraction_threshold_walking_to_bicycling.png}}

\caption{Matched-filter performance comparing jogging and bicycling data against a reference for walking. Results produced at decimation 8. Figures (c) and (d) are the corresponding ROC curves produced from (a) and (b) respectively.}
  \label{fig:MF_performance}
\end{figure}
